Left-linear rewriting in adhesive categories

### 2024-04-23 concur/fusione.tex
typo

\begin{example}
  \label{ex:non-global}
  Consider a new rewriting system in $\cat{Graph}$ consisting of the
  rules in $\sigma_0$, $\sigma_1$, and $\sigma_2$ in
  Fig.~\ref{fi:rules-cas}.
  %\todo{P: rev.2 dice ``In the top-left and
   % top-middle nodes of $\rho_3$, the labels "12" should be "1" and
   % "2".''. Non e' corretto, ma magari si capisce poco ...}  
   Consider the derivation $\der{F}$ in Fig.~\ref{fi:derF}. Note that rule
  $\sigma_2$ needs the black self-loop on node $12$ to be applied. This can be
  generated either by $\sigma_0$ or by $\sigma_1$ merging nodes $1$ and
  $2$, hence at least one of them must precede the application of
  $\sigma_2$. Indeed, in $\der{F}$ it can be easily seen that the second
  and the third step applying $\sigma_1$ and $\sigma_2$ are
  independent. However, we could switch twice the application of
  $\sigma_0$, bringing it in the last position, obtaining a derivation
  $\der{F}'$ as depicted in Fig.~\ref{fi:derF1}, where the
  applications of $\sigma_1$ and $\sigma_2$ are no longer independent.

>>>>

\begin{example}
  \label{ex:non-global}
  Consider a new rewriting system in $\cat{Graph}$ consisting of the
  rules $\sigma_0$, $\sigma_1$, and $\sigma_2$ in
  Fig.~\ref{fi:rules-cas}.
  %\todo{P: rev.2 dice ``In the top-left and
   % top-middle nodes of $\rho_3$, the labels "12" should be "1" and
   % "2".''. Non e' corretto, ma magari si capisce poco ...}  
   Consider the derivation $\der{F}$ in Fig.~\ref{fi:derF}. Note that rule
  $\sigma_2$ needs the black self-loop on node $12$ to be applied. This can be
  generated either by $\sigma_0$ or by $\sigma_1$ merging nodes $1$ and
  $2$, hence at least one of them must precede the application of
  $\sigma_2$. Indeed, in $\der{F}$ it can be easily seen that the second
  and the third step applying $\sigma_1$ and $\sigma_2$ are
  independent. However, we could switch twice the application of
  $\sigma_0$, bringing it in the last position, obtaining a derivation
  $\der{F}'$ as depicted in Fig.~\ref{fi:derF1}, where the
  applications of $\sigma_1$ and $\sigma_2$ are no longer independent.
